Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-04-10 WRITEUP/ms.tex
alpha_vir for 8 ss, double check ss order

\begin{figure*}
% \centering
\includegraphics[width=\textwidth]{\figpath/alpha_vir_ss21-ss22.png}
% \includegraphics[width=0.925\textwidth]{\figpath/alpha_vir-stellar_to_gas_ss21-ss22.png}
\caption{
% Top: 
Virial parameter and mass of MCCs in the pre-starburst (left) and starburst phase (right) of \flower. 
% Bottom: $\alpha_{\rm vir}$ and stellar-to-gas mass ratio of MCCs.
Definition of the symbol shown are the same as in \Fig{larsons_single}.
Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$ of MCCs in \flower. 
Excluding the biggest MCCs, MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
% Overall, the stellar-to-gas mass ratio of MCCs in the starburst phase is higher. 
\label{fig:alpha21-22}}
\end{figure*}

@@

% Starburst 
In the starburst phase, MCCs have velocity dispersion, sizes,
and virial parameter comparable to those in the accreting phase; however, the MCCs in the starburst phase span 
a wider range in $\sigma^2/R$ and gas surface density. 
Due to a time delay between cloud collapse and \SF, we also examine the virial parameter of MCCs in the pre-starburst phase. 
As shown in \Fig{alpha21-22}, the total virial parameter (blue dots in the figure) 
of a subset of MCCs in the pre-starburst phase are lower than those in the starburst phase of the same mass range, which is as expected.
%Similarly, the stellar-to-gas mass ratio of MCCs in the starburst phase is higher overall (see bottom panels of \Fig{alpha21-22}).
%These trends are as expected in the MCC properties prior to and during a starburst. 
% None of these MCCs are in the unstable regime ($alpha_{\rm vir} < 2$) because the MCCs are not directly the collapsing structures, 
% i.e., we haven’t reached those scales where true collapse is happening. 
% This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.
As shown in \Fig{Mach_stellarRatio}, the Mach number (see Equation~\ref{eqn:MPress}) 
of MCCs with a stellar-to-gas mass ratio of $M_\star/M_{\rm gas} \simeq 0.1 - 1$ 
(i.e., excluding the main component of \flower with $M_\star/M_{\rm gas} \gtrsim 1$; see e.g., \Fig{stellarRatio16})
increases from the pre-starburst phase through the post-starburst phase. 
This results as stellar feedback injects kinetic energy into the surrounding ISM in the form of turbulence as \SF proceed.
In the quiescent phase, high Mach number are seen in mostly MCCs identified with the lowest density threshold. These 
correspond to satellites MCCs in the outskirts of \flower.

@@

\DL{
1) Add to discussion in Sec 6.3? As shown in alphavir total, the high stellar-to-gas mass ratio, 
influence from the stellar component plays a non-negligible role, as seen in Toomre Q analysis.
% 
2) TODO: Add a plot showing the different alphavir over time. Add a line somewhere that feedback plays in important role in the virial parameter, as 
can be seen in the strong variation in alphavir across the different evolutionary stages of \flower. 
and also the increase in $M$ as \SF proceed in \flower, see \Fig{Mach_stellarRatio}.
% 
3) overall lower alphavir in the pre-SB phase in \Fig{alpha21-22}. 
1) the general trend is consistent with physics -- alphavir of MCCs are lower compared to other snapshots in the pre-SB phase.  
The reason that we don’t see any MCCs with alphavir $<$ 2 can be understood by realizing that the MCCs are not 
directly the collapsing structures, i.e., we haven’t reached those scales where true collapse is happening.
This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.
}

>>>>

%\begin{figure*}
%% \centering
%\includegraphics[width=\textwidth]{\figpath/alpha_vir_ss21-ss22.png}
%% \includegraphics[width=0.925\textwidth]{\figpath/alpha_vir-stellar_to_gas_ss21-ss22.png}
%\caption{
%% Top: 
%Virial parameter and mass of MCCs in the pre-starburst (left) and starburst phase (right) of \flower. 
%% Bottom: $\alpha_{\rm vir}$ and stellar-to-gas mass ratio of MCCs.
%Definition of the symbol shown are the same as in \Fig{larsons_single}.
%Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$ of MCCs in \flower. 
%Excluding the biggest MCCs, MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
%% Overall, the stellar-to-gas mass ratio of MCCs in the starburst phase is higher. 
%\label{fig:alpha21-22}}
%\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/alpha_vir_ss16-ss23.png}
\caption{Virial parameter as a function of MCC mass for different evolutionary stages of \flower, beginning from the accreting phase (top left).
Evolutionary stages are shown chronologically from top left to bottom left, followed by top right to bottom right.
Definition of symbols shown are the same as in \Fig{larsons_single}.
Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$.
Excluding the biggest MCCs (see \Fig{stellarRatio16} and \Sec{singless}), 
MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
The virial parameter vary over the $\sim$300\,Myr shown here, as \flower\ evolves.
The variation is clearly seen between the pre-starburst through post-starburst phase. 
\label{fig:alphaEvol}}
\end{figure*}
{\bf CHECK if I am plotting the righ alphaVIR snapshots../.}

@@

% Starburst 
In the starburst phase, MCCs have velocity dispersion, sizes,
and virial parameter comparable to those in the accreting phase; however, the MCCs in the starburst phase span 
a wider range in $\sigma^2/R$ and gas surface density. 
Due to a time delay between cloud collapse and \SF, we also examine the virial parameter of MCCs in the pre-starburst phase. 
As shown in \Fig{alphaEvol}, the total virial parameter (blue dots in the figure) 
of a subset of MCCs in the pre-starburst phase are lower than those in the starburst phase of the same mass range, which is as expected.
%Similarly, the stellar-to-gas mass ratio of MCCs in the starburst phase is higher overall (see bottom panels of \Fig{alpha21-22}).
%These trends are as expected in the MCC properties prior to and during a starburst. 
% None of these MCCs are in the unstable regime ($alpha_{\rm vir} < 2$) because the MCCs are not directly the collapsing structures, 
% i.e., we haven’t reached those scales where true collapse is happening. 
% This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.
As shown in \Fig{Mach_stellarRatio}, the Mach number (see Equation~\ref{eqn:MPress}) 
of MCCs with a stellar-to-gas mass ratio of $M_\star/M_{\rm gas} \simeq 0.1 - 1$ 
(i.e., excluding the main component of \flower with $M_\star/M_{\rm gas} \gtrsim 1$; see e.g., \Fig{stellarRatio16})
increases from the pre-starburst phase through the post-starburst phase. 
This results as stellar feedback injects kinetic energy into the surrounding ISM in the form of turbulence as \SF proceed.
In the quiescent phase, high Mach number are seen in mostly MCCs identified with the lowest density threshold. These 
correspond to satellites MCCs in the outskirts of \flower.

@@

\DL{
1) Add to discussion in Sec 6.3? As shown in alphavir total, the high stellar-to-gas mass ratio, 
influence from the stellar component plays a non-negligible role, as seen in Toomre Q analysis.
% 
2) TODO: Add a plot showing the different alphavir over time. Add a line somewhere that feedback plays in important role in the virial parameter, as 
can be seen in the strong variation in alphavir across the different evolutionary stages of \flower. 
and also the increase in $M$ as \SF proceed in \flower, see \Fig{Mach_stellarRatio}.
% 
3) overall lower alphavir in the pre-SB phase in \Fig{alphaEvol}. 
1) the general trend is consistent with physics -- alphavir of MCCs are lower compared to other snapshots in the pre-SB phase.  
The reason that we don’t see any MCCs with alphavir $<$ 2 can be understood by realizing that the MCCs are not 
directly the collapsing structures, i.e., we haven’t reached those scales where true collapse is happening.
This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.
}
